### 2022-09-22 main/chapter_context.tex
diameter to radius; add atlas proposal

\subsection{Design}
Atlas is a Titan.
On the \cern\ Large Hadron Collider (LHC), \atlas\ is the largest detector
experiment, and alongside its big neighbours
\cms~\cite{cms2008experiment},
\lhcb~\cite{lhcb2008experiment},
and ALICE~\cite{alice2008experiment}
it is a multi-kilotonne beast,
and a wonder of scientific engineering~\cite{
atlas2008experiment,
atlas1999design1,
atlas1999design2
}.

@@

Measurements of the tracks' curvature yield estimates of the muons' momenta;
although extremely energetic muons will have straight tracks,
\atlas' design and calibration achieves a high precision that increases to
only $10\%$ relative error on tracks with $1\,\eV[T]$ transverse momenta~\cite{
atlas2008experiment,
ATL-PHYS-PUB-2015-037
}.

\subsection{Trigger}
\label{sec:atlas_trigger}
\TODO{L1 HLT (L2, event thing)}
\TODO{trigger~\cite{atlas2016trigger}}
% 25ns bunch spacing
\TODO{
With $25\,\mathrm{ns}$ bunch spacing and \atlas' $25\,\textrm{m}$ diameter,
light-speed particles ejected from one crossing are still zipping through
\atlas\ when the next crossing happens.
}
% fast decisions to not overflow buffer queue
\begin{quote}
``%
A two-level trigger system is used to select events.
The first-level trigger is implemented in hardware and uses a subset of the
detector information to accept events at a rate below $100\,\mathrm{kHz}$.
This is followed by a software-based trigger that reduces the accepted event
rate to $1\,\mathrm{kHz}$ on average depending on the data-taking conditions.%
''~\cite{atlas2022searches}
\end{quote}

>>>>

\subsection{Design}
Atlas is a Titan.
On the \cern\ Large Hadron Collider (LHC), \atlas\ is the largest detector
experiment, and alongside its biggest neighbours
\cms~\cite{cms2008experiment},
\lhcb~\cite{lhcb2008experiment},
and ALICE~\cite{alice2008experiment}
it is a multi-kilotonne beast,
and a wonder of scientific engineering~\cite{
atlas1994proposal,
atlas2008experiment,
atlas1999design1,
atlas1999design2
}.

@@

Measurements of the tracks' curvature yield estimates of the muons' momenta;
although extremely energetic muons will have straight tracks,
\atlas' design and calibration achieves a high precision that increases to
only $10\%$ relative error on tracks with $1\,\eV[T]$ transverse momenta~\cite{
atlas1994proposal,
atlas2008experiment,
ATL-PHYS-PUB-2015-037
}.

\subsection{Trigger}
\label{sec:atlas_trigger}
\TODO{L1 HLT (L2, event thing)}
\TODO{trigger~\cite{atlas2016trigger}}
% 25ns bunch spacing
\TODO{
With $25\,\mathrm{ns}$ bunch spacing and \atlas' $12.5\,\textrm{m}$ radius,
light-speed particles ejected from one crossing are still zipping through
\atlas\ when the next collision arrives.
}
% fast decisions to not overflow buffer queue
\begin{quote}
``%
A two-level trigger system is used to select events.
The first-level trigger is implemented in hardware and uses a subset of the
detector information to accept events at a rate below $100\,\mathrm{kHz}$.
This is followed by a software-based trigger that reduces the accepted event
rate to $1\,\mathrm{kHz}$ on average depending on the data-taking conditions.%
''~\cite{atlas2022searches}
\end{quote}
